Annotation exploration for SCPCP000006, `predicted.score` threshold `r params$predicted.score_thr`

### 2024-11-14 analyses/cell-type-wilms-tumor-06/notebook/04_annotation_Across_Samples_exploration.Rmd
revert some of the sample_id code

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")

metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE) |>
  dplyr::filter(seq_unit != "spot")

# Create a data frames of all annotations
cell_type_df <- metadata$scpca_sample_id |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("02b-fetal_kidney_label-transfer_{sample_id}.Rds")
      )

>>>>

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")
metadata <- read_tsv(sample_metadata_file) |>
  dplyr::filter(seq_unit != "spot")

# Create a data frames of all annotations
cell_type_df <- metadata$scpca_sample_ids |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("02b-fetal_kidney_label-transfer_{sample_id}.Rds")
      )
